openTSNE: a modular \proglang{Python} library for t-SNE dimensionality reduction and embedding

### 2023-05-23 2023-05-revision-1/main.tex
paper: describe BH/FFT heuristic

\item In optimizing the embedding, the t-SNE algorithm finds the positions of the points in the embedding space that reflect their corresponding similarities in the affinity model. \opentsne stores the initial positions and affinities in a \code{openTSNE.TSNEEmbedding} object that includes the \code{.optimize} method for embedding optimization that uses either the Barnes-Hut or FIt-SNE approximation scheme. While the FIt-SNE approximation scheme scales linearly with the number of samples, it introduces additional computational overhead, often unnecessary for smaller data sets, resulting in longer runtimes than the Barnes-hut approximation scheme. By default, \opentsne uses a heuristic to choose the fastest algorithm for a given data set.
\end{enumerate}

>>>>

\item In optimizing the embedding, the t-SNE algorithm finds the positions of the points in the embedding space that reflect their corresponding similarities in the affinity model. \opentsne stores the initial positions and affinities in an \code{openTSNE.TSNEEmbedding} object that includes the \code{.optimize} method for embedding optimization that uses either the Barnes-Hut or FIt-SNE approximation scheme. While the FIt-SNE approximation scheme scales linearly with the number of samples, it introduces additional computational overhead, often unnecessary for smaller data sets, resulting in longer overall runtimes than the Barnes-Hut approximation scheme. By default, \opentsne uses an empirically-determined heuristic to choose the fastest algorithm for a given data set based on its number of samples. If the data set contains fewer than 10,000 samples, the Barnes-Hut approximation scheme is selected, while FIt-SNE is used for larger data sets.

\end{enumerate}
